```{r}
library(ggplot2)
library(tidyverse)
library(MASS)
library(janitor)
library(dplyr)
library(pROC)
library(irr)
library(reshape2)
library(caret)

# Useful function: Cross-validation for LDA and QDA
cross_validate <- function(model_formula, data, k = 5, method = "lda") {
    set.seed(123) # Set seed for reproducibility
    
    # Create k-folds
    folds <- sample(rep(1:k, length.out = nrow(data)))
    
    # Initialize a list to store results and models
    results <- list()
    models <- list()
    
    # Perform cross-validation
    for (i in 1:k) {
        # Split data into training and testing sets
        train_data <- data[folds != i, ]
        test_data <- data[folds == i, ]
        
        # Train the model
        model <- if (method == "lda") {
            lda(formula = model_formula, data = train_data)
        } else if (method == "qda") {
            qda(formula = model_formula, data = train_data)
        } else {
            stop("Unsupported method. Use 'lda' or 'qda'.")
        }
        
        # Predict on the testing set
        predictions <- predict(model, test_data)$class
        
        # Calculate metrics
        confusion <- table(predictions, test_data$diabetes_012)
        accuracy <- sum(diag(confusion)) / sum(confusion)
        precision <- diag(confusion) / rowSums(confusion)
        precision[is.na(precision)] <- 0
        recall <- diag(confusion) / colSums(confusion)
        recall[is.na(recall)] <- 0
        f1 <- 2 * (precision * recall) / (precision + recall)
        f1[is.na(f1)] <- 0
        
        # Calculate kappa
        confusion_df <- as.data.frame(as.table(confusion))
        kappa <- kappam.fleiss(confusion_df)$value
        
        # Store the result and model
        results[[i]] <- list(
            accuracy = accuracy,
            precision = precision,
            recall = recall,
            f1 = f1,
            kappa = kappa
        )
        models[[i]] <- model
    }
    
    return(list(models = models, results = results))
}

# Multi-class evaluation
eval_multi_class <- function(conf_matrix) {
    cc <- sum(diag(conf_matrix))
    sc <- sum(conf_matrix)
    pp <- colSums(conf_matrix)
    tt <- rowSums(conf_matrix)
    
    prec <- diag(conf_matrix) / pp
    prec[is.na(prec)] <- 0
    recall <- diag(conf_matrix) / tt
    recall[is.na(recall)] <- 0
    macro_prec <- mean(prec, na.rm = TRUE)
    macro_recall <- mean(recall, na.rm = TRUE)
    macro_f1 <- 2 * macro_prec * macro_recall / (macro_prec + macro_recall)
    acc <- cc / sc
    kap <- (cc * sc - sum(pp * tt)) / (sc^2 - sum(pp * tt))
    
    return(list(Precision = prec, Recall = recall, Accuracy = acc, Kappa = kap, Macro_F1 = macro_f1))
}

# Evaluate models with enhanced flexibility
evaluate_models <- function(train_data, test_data) {
    # LDA cross-validation
    lda_results <- cross_validate(diabetes_012 ~ ., train_data, method = "lda")
    lda_avg_results <- sapply(lda_results$results, function(res) sapply(res, mean))
    
    # QDA cross-validation
    qda_results <- cross_validate(diabetes_012 ~ ., train_data, method = "qda")
    qda_avg_results <- sapply(qda_results$results, function(res) sapply(res, mean))
    
    # Determine the best model based on F1 score
    best_model <- ifelse(mean(lda_avg_results["f1", ]) > mean(qda_avg_results["f1", ]), "LDA", "QDA")
    
    # Train final models
    final_lda_model <- lda(diabetes_012 ~ ., data = train_data)
    final_qda_model <- qda(diabetes_012 ~ ., data = train_data)
    
    # Predict on test data
    lda_predictions <- predict(final_lda_model, test_data)$class
    qda_predictions <- predict(final_qda_model, test_data)$class
    
    # Create confusion matrices
    lda_confusion <- table(test_data$diabetes_012, lda_predictions)
    qda_confusion <- table(test_data$diabetes_012, qda_predictions)
    
    # Evaluate metrics
    lda_metrics <- eval_multi_class(lda_confusion)
    qda_metrics <- eval_multi_class(qda_confusion)
    
    # Compile results
    results <- data.frame(
        Metric = c("Accuracy", "Precision", "Recall", "F1", "Kappa"),
        LDA = c(lda_metrics$Accuracy, mean(lda_metrics$Precision, na.rm = TRUE), mean(lda_metrics$Recall, na.rm = TRUE), lda_metrics$Macro_F1, lda_metrics$Kappa),
        QDA = c(qda_metrics$Accuracy, mean(qda_metrics$Precision, na.rm = TRUE), mean(qda_metrics$Recall, na.rm = TRUE), qda_metrics$Macro_F1, qda_metrics$Kappa)
    )
    
    # Visualize results
    metrics_data <- melt(results, id.vars = "Metric")
    
    ggplot(metrics_data, aes(x = Metric, y = value, fill = variable)) +
        geom_bar(stat = "identity", position = "dodge") +
        labs(title = "Performance Metrics for LDA and QDA Models",
             x = "Metric",
             y = "Value") +
        theme_minimal()
    
    return(list(results = results, lda_predictions = lda_predictions, qda_predictions = qda_predictions))
}

plot_confusion_matrix <- function(conf_matrix, model_name) {
    conf_matrix_df <- as.data.frame(conf_matrix)
    colnames(conf_matrix_df) <- c("Actual", "Predicted", "Freq")
    
    ggplot(conf_matrix_df, aes(x = Actual, y = Predicted, fill = Freq)) +
        geom_tile() +
        geom_text(aes(label = Freq), color = "white") +
        scale_fill_gradient(low = "lightblue", high = "lightcoral") +
        labs(title = paste("Confusion Matrix -", model_name, "Predictions"), x = "Actual", y = "Predicted") +
        theme_minimal()
}
```


```{r}
train_data = read.csv("data/train_data.csv")
test_data = read.csv("data/test_data.csv")
```


```{r}
glimpse(train_data)
```


## Data Preprocessing


```{r}
train_data <- train_data |> mutate(across(everything(), as.factor))
test_data <- test_data |> mutate(across(everything(), as.factor))
```


```{r}
glimpse(train_data)
```


```{r}
print(table(train_data$diabetes_012))
print(table(test_data$diabetes_012))
```


## Modeling


### Thử trên data gốc


```{r}
results = evaluate_models(train_data, test_data)
```


```{r}
conf_matrix <- table(test_data$diabetes_012, results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

plot_confusion_matrix(conf_matrix, "LDA")
```


```{r}
conf_matrix <- table(test_data$diabetes_012, results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)
plot_confusion_matrix(conf_matrix, "QDA")
```


### Thử trên Data Oversampling


```{r}
oversampling_data <- read.csv("data/oversampled_data.csv")
oversampling_data <- oversampling_data |> mutate(across(everything(), as.factor))

glimpse(oversampling_data)
```


```{r}
table(oversampling_data$diabetes_012)
```


#### Train với thông số cơ bản


```{r}
oversampling_results <- evaluate_models(oversampling_data, test_data)
```


```{r}
conf_matrix <- table(test_data$diabetes_012, oversampling_results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


```{r}
conf_matrix <- table(test_data$diabetes_012, oversampling_results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)
# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Thử trên Data Undersampling


```{r}
undersampling_data <- read.csv("data/undersampled_data.csv")
undersampling_data <- undersampling_data |> mutate(across(everything(), as.factor))

glimpse(undersampling_data)

table(undersampling_data$diabetes_012)
```


#### Train với thông số cơ bản


```{r}
train_without_cross <- function(train_data, test_data) {
    # Train LDA model on train_data
    lda_model <- lda(diabetes_012 ~ ., data = train_data)
    
    # Predict on train_data
    lda_predictions_train <- predict(lda_model, train_data)$class
    lda_pred_probs_train <- predict(lda_model, train_data)$posterior
    
    # Calculate confusion matrix and metrics for training data
    lda_conf_matrix_train <- table(train_data$diabetes_012, lda_predictions_train)
    lda_metrics_train <- eval_multi_class(lda_conf_matrix_train)
    
    # Print metrics for training data
    cat("LDA Training Metrics:\n")
    print(lda_metrics_train)
    
    # Predict on test_data
    lda_predictions <- predict(lda_model, test_data)$class
    lda_pred_probs <- predict(lda_model, test_data)$posterior
    
    # Train QDA model on train_data
    qda_model <- qda(diabetes_012 ~ ., data = train_data)
    
    # Predict on train_data
    qda_predictions_train <- predict(qda_model, train_data)$class
    qda_pred_probs_train <- predict(qda_model, train_data)$posterior
    
    # Calculate confusion matrix and metrics for training data
    qda_conf_matrix_train <- table(train_data$diabetes_012, qda_predictions_train)
    qda_metrics_train <- eval_multi_class(qda_conf_matrix_train)
    
    # Print metrics for training data
    cat("QDA Training Metrics:\n")
    print(qda_metrics_train)
    
    # Predict on test_data
    qda_predictions <- predict(qda_model, test_data)$class
    qda_pred_probs <- predict(qda_model, test_data)$posterior
    
    # Return predictions and probabilities for both models
    return(list(
        lda_predictions = lda_predictions,
        lda_pred_probs = lda_pred_probs,
        qda_predictions = qda_predictions,
        qda_pred_probs = qda_pred_probs
    ))
}

undersampling_results <- train_without_cross(undersampling_data, test_data)
```


Cho LDA


```{r}
conf_matrix <- table(test_data$diabetes_012, undersampling_results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(test_data$diabetes_012, undersampling_results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Thử trên Data SMOTE Sampling


```{r}
smote_data <- read.csv("data/smote_augmented_data_80_percent.csv")
smote_data <- smote_data |> mutate(across(everything(), as.factor))

glimpse(smote_data)
table(smote_data$diabetes_012)
```


### Train với thông số cơ bản


```{r}
smote_results <- evaluate_models(smote_data, test_data)
```


```{r}
conf_matrix <- table(test_data$diabetes_012, smote_results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


```{r}
conf_matrix <- table(test_data$diabetes_012, smote_results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


## Modeling With Binary 0 & {1, 2}


```{r}
convert_to_binary <- function(data) {
    data |> mutate(diabetes_012 = ifelse(diabetes_012 %in% c(1, 2), 1, ifelse(diabetes_012 == 0, 0, diabetes_012)))
}


binary_train_data <- convert_to_binary(train_data)
binary_oversampling_data <- convert_to_binary(oversampling_data)
binary_undersampling_data <- convert_to_binary(undersampling_data)
binary_smote_data <- convert_to_binary(smote_data)
binary_test_data <- convert_to_binary(test_data)
```


```{r}
table(binary_train_data$diabetes_012)
table(binary_test_data$diabetes_012)
```


### Train Data


```{r}
binary_results <- evaluate_models(binary_train_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, binary_results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, binary_results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Oversampling Data


```{r}
oversampling_results_binary <- evaluate_models(binary_oversampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, oversampling_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, oversampling_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Undersampling Data


```{r}
undersampling_results_binary <- evaluate_models(binary_undersampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, undersampling_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, undersampling_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### SMOTE Data


```{r}
smote_results_binary <- evaluate_models(binary_smote_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, smote_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, smote_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```

## Modeling with Binary 1 & {0, 2}

Class 0 và 2 sẽ được biến đổi thành class 1 và class 1 sẽ được chỉnh thành 0.

```{r}
convert_to_binary <- function(data) {
    data |> mutate(diabetes_012 = ifelse(diabetes_012 %in% c(0, 2), 1, ifelse(diabetes_012 == 1, 0, diabetes_012)))
}

binary_train_data <- convert_to_binary(train_data)
binary_oversampling_data <- convert_to_binary(oversampling_data)
binary_undersampling_data <- convert_to_binary(undersampling_data)
binary_smote_data <- convert_to_binary(smote_data)
binary_test_data <- convert_to_binary(test_data)
```


```{r}
table(binary_train_data$diabetes_012)
table(binary_test_data$diabetes_012)
```


### Train Data


```{r}
binary_results <- evaluate_models(binary_train_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, binary_results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, binary_results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Oversampling Data


```{r}
oversampling_results_binary <- evaluate_models(binary_oversampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, oversampling_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, oversampling_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Undersampling Data


```{r}
undersampling_results_binary <- train_without_cross(binary_undersampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, undersampling_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, undersampling_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### SMOTE Data


```{r}
smote_results_binary <- evaluate_models(binary_smote_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, smote_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, smote_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```

## Modeling with Binary 2 & {0, 1}

Class 0 và 1 biến đổi thành class 1 và class 2 được biến đổi thành class 1

```{r}
convert_to_binary <- function(data) {
    data |> mutate(diabetes_012 = ifelse(diabetes_012 %in% c(0, 1), 0, ifelse(diabetes_012 == 2, 1, diabetes_012)))
}

binary_train_data <- convert_to_binary(train_data)
binary_oversampling_data <- convert_to_binary(oversampling_data)
binary_undersampling_data <- convert_to_binary(undersampling_data)
binary_smote_data <- convert_to_binary(smote_data)
binary_test_data <- convert_to_binary(test_data)
```


```{r}
table(binary_train_data$diabetes_012)
table(binary_test_data$diabetes_012)
```


### Train Data


```{r}
binary_results <- evaluate_models(binary_train_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, binary_results$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, binary_results$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Oversampling Data


```{r}
oversampling_results_binary <- evaluate_models(binary_oversampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, oversampling_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, oversampling_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### Undersampling Data


```{r}
undersampling_results_binary <- evaluate_models(binary_undersampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, undersampling_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, undersampling_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```


### SMOTE Data


```{r}
smote_results_binary <- evaluate_models(binary_undersampling_data, binary_test_data)
```


Cho LDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, smote_results_binary$lda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "LDA")
```


Cho QDA


```{r}
conf_matrix <- table(binary_test_data$diabetes_012, smote_results_binary$qda_predictions)
conf_matrix

eval_multi_class(conf_matrix)

# Plot confusion matrix using the function
plot_confusion_matrix(conf_matrix, "QDA")
```
